LAGOS lake depth

### 2020-11-23 figures/01_contrasts.Rmd
more name change propagation

```{r gg_slope_shape_class, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
gg_slope_shape_class <- dt %>%
  dplyr::filter(shape_class != "neither") %>%  
  contrast_plot(grp = "shape_class", varb = "inlake_slope", 
                label = "In-lake slope (m/m)", plot_type = "pointrange")
```

@@

```{r gg_slope_reservoir, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
gg_slope_reservoir <- dt %>%
  dplyr::filter(!is.na(reservoir_class)) %>%  
  contrast_plot(grp = "reservoir_class", varb = "inlake_slope", 
                label = "In-lake slope (m/m)", plot_type = "pointrange")
```

@@

```{r gg_shorelinedev_shape_class, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
# compare shoreline dev for each shapeclass
gg_shorelinedev_shape_class <- dt %>%
  dplyr::filter(shape_class != "neither") %>%  
  contrast_plot(grp = "shape_class", varb = "lake_shorelinedevfactor_nounits", 
                label = "Shoreline Dev.", plot_type = "pointrange")
```

@@

lg$urban_distance <- apply(
  st_distance(
    st_transform(
      LAGOSUS::coordinatize(lg, crs = 4326), 
      LAGOSUSgis:::albers_conic()),
    urbanareas), 
  1, function(x) x[which.min(x)])
lg$urban_distance <- lg$urban_distance * 0.001 # m to km

>>>>

```{r gg_slope_shape_class, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
gg_slope_shape_class <- dt %>%
  dplyr::filter(shape_class != "neither") %>%  
  contrast_plot(grp = "shape_class", varb = "inlake_slope_pnt", 
                label = "In-lake slope (m/m)", plot_type = "pointrange")
```

@@

```{r gg_slope_reservoir, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
gg_slope_reservoir <- dt %>%
  dplyr::filter(!is.na(reservoir_class)) %>%  
  contrast_plot(grp = "reservoir_class", varb = "inlake_slope_pnt", 
                label = "In-lake slope (m/m)", plot_type = "pointrange")
```

@@

```{r gg_shorelinedev_shape_class, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
# compare shoreline dev for each shapeclass
gg_shorelinedev_shape_class <- dt %>%
  dplyr::filter(shape_class != "neither") %>%  
  contrast_plot(grp = "shape_class", varb = "lake_shorelinedevfactor", 
                label = "Shoreline Dev.", plot_type = "pointrange")
```

@@

lg$urban_distance <- apply(
  st_distance(
    st_transform(
      LAGOSUS::coordinatize(dt = lg, crs_in = 4326), 
      LAGOSUSgis:::albers_conic()),
    urbanareas), 
  1, function(x) x[which.min(x)])
lg$urban_distance <- lg$urban_distance * 0.001 # m to km
